Supplement

### 2023-04-26 paper/manuscript.tex
work on intro and figure 2

\hypertarget{introduction}{%
\section{introduction}\label{introduction}}

When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down. Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy. Results that cannot be observed consistently are like dirt clots, they don't hold their shape and thus are not a strong foundation for the theories and studies built on top of them. Replications and the theory of replicability can be thought of as a way of testing whether the empirical results are sturdy. Replicating is a necessary feature for load-bearing empirical results. We note that replicability is not the only desirable feature of a study, and that replicating does not mean that a study is valid, or generalizable, or interesting.

A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed. This is illustrated both by a few prominent findings that turn out to not replicate at all {[}ex. terror management theory; Klein et al. (\protect\hyperlink{ref-klein2022}{2022}){]}, and by large-scale replication projects such as RP:P which found a replication rate around 40\% for a sample of the psychology literature (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.

A big open question is why the replication rates in psychology are so low. There are theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE). There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.

A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate. For instance, across 16 studies, Protzko et al. (\protect\hyperlink{ref-protzko2020}{2020}) showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original. Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.

As an alternative, much of the work looking at predictors of replicability has been correlation: whether using regression models, prediction markets, or machine learning techniques to build predictions about what will replicate. However, all of these approaches depend on data from replications. While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points from large-scale replication projects. The RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}). These correlational approaches have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al. 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al. 2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al. 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al. 2019}), but have not identified that many concrete predictors that differentiate replications from non-replications. In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.

This reliance on the same small set of data is problematic, as much of what we think we know about replicability is overfit to this small sample. However, given the time-consuming nature of running a large number of replications, there is a limited amount of large-scale replication data to draw on. We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). The ManyLabs series of replications investigating heterogeneity has sampled target studies that are short and compare only two conditions, which is not representative of the psychology literature as a whole. Across Many Labs 1-3, 29 of 51 target effects (57\%) were found to replicate (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) found a roughly 60\% replication rate when they replicated all 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. Those are all the large-scale replication projects of experimental psychology results available at this time. These roughly 170 results are heavily represented in the work predicting what effects will replicate.

The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap. Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-wagge2019}{Wagge et al. 2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}, \protect\hyperlink{ref-hawkins}{Hawkins et al. n.d.}). {[}TODO needs transition{]}

Our main contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al. 2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al. n.d.}).

@@

The sampling for our replications is based on what studies students were interested in and wanted to replicate, with some constraints of feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable within their ability and budgetary constraints. Our primary criteria for replication success is a subjective measure of whether the study replicated for the same reason, that we believe this is usually what researchers care about: is it close enough that you think you're getting at the same effect and could confidently build on it. The quality of the replications also reflects this: unlike some prior work like Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}), which explicitly aimed for high-powered replications, the power in these studies was limited by budgetary reasons in some cases, which is reflective of the types of resources often available to trainee scientists.

We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?

@@

Many different measures can be used to define replication success of an individual statistical result, and there is much discussion over what each measure represents and which make sense (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure. This measure has the benefit that it was applicable across the diverse range of statistical measures and reporting practices present in the sample. It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest. A holistic measure of replication success had been coded for each project when it was turned in at the end of the class. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (25.5681818 \% of cases).

@@

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.4390244 times the rate of social psychology studies. Within and between subjects designs were both common, and within replicated 3.35 times as much. Similarly, studies with multiple vignettes replicated 2.6315789 times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

@@

Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person). While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{Crump et al. 2013})TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

@@

While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another. In order to determine which predictors were the strongest, we ran a pre-registered regularized regression model (see Methods for details). The coefficient estimates are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients. The general directions of coefficients are consistent with the effects of the predictors in isolation. Within-subjects designs seem an especially strong indicator of replicability (0.55{[}-0.01,2{]}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-crump2013}{}}%
Crump MJC, McDonnell JV, Gureckis TM (2013) Evaluating {Amazon}'s {Mechanical Turk} as a {Tool} for {Experimental Behavioral Research} (S Gilbert, Ed.). \emph{PLoS ONE} \textbf{8}:e57410. doi:\href{https://doi.org/10.1371/journal.pone.0057410}{10.1371/journal.pone.0057410}

@@

\leavevmode\vadjust pre{\hypertarget{ref-frank2012}{}}%
Frank MC, Saxe R (2012) Teaching {Replication}: \emph{Perspect Psychol Sci}. doi:\href{https://doi.org/10.1177/1745691612460686}{10.1177/1745691612460686}

@@

\leavevmode\vadjust pre{\hypertarget{ref-quintana2021}{}}%
Quintana DS (2021) Replication studies for undergraduate theses to improve science and education. \emph{Nat Hum Behav} \textbf{5}:1117--1118. doi:\href{https://doi.org/10.1038/s41562-021-01192-8}{10.1038/s41562-021-01192-8}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wagge2019}{}}%
Wagge JR, Brandt MJ, Lazarevic LB, Legate N, Christopherson C, Wiggins B, Grahe JE (2019) \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00247}{Publishing {Research With Undergraduate Students} via {Replication Work}: {The Collaborative Replications} and {Education Project}}. \emph{Front Psychol} \textbf{10}

>>>>

introduction outline:

Things don't replicate that well and it feels like a problem for cumulative science
* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up.
* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate. Called into question reliability of literature as a whole -- lead to a few measurements.
* Large scale replications of chunks of the literature, but aren't many (list and explain)
* These rates feel lower than we want

Why? Many approaches, no definitive answers.
* Why are rates what they are. Both want to know to fix but also to watch out / calibrate caution. Can be approached from theoretical, interventional, and correlational dimensions.
* Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
* Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
* Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
- Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory \& intervention. (Interplay between them)

What's missing from the conversation and why our approach is good.
* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available). Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.
* Don't want to build on something and fail a bunch trying to get your variant to work and then realize it just doesn't work. Replicability (as we mean it here) A useful framing is ``ability to do cumulative science'' -- close to what people mean, may disagree with many things
* How this approach differs and what it gets us
* (built in feasibility under reasonable / small resource constraints)
* interest based sampling
* functional approach sidesteps issues of ``truth'' (may even be reliable in a different environment, but would be)

Teaser:
* We do x,y,z, and find that larger effect sizes and within subjects designs are the two strongest correlates of replicability in this sample.

Questions:
- mention primary outcome in intro?
- switch out fig 4 for supp fig 2?
- do we want to use the term p(cumulative)?

TODO fill in cites
flesh out theoretical approaches section

introduction outline:

Things don't replicate that well and it feels like a problem for cumulative science
* For a cumulative science, we want (many) of the load-bearing empirical results that form the bases of theories to hold up.
For a cumulative science, the empirical results that form the bases for theories and
* People were acting as if publication of results meant they were true/reliable, trying to build on things; caused crises when some prominent results failed to replicate. Called into question reliability of literature as a whole -- lead to a few measurements.
A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed. This is illustrated both by a few prominent findings that turn out to not replicate at all {[}ex. terror management theory; Klein et al. (\protect\hyperlink{ref-klein2022}{2022}){]}, and by large-scale replication projects such as RP:P which found a replication rate around 40\% for a sample of the psychology literature (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.

\begin{itemize}
\tightlist
\item
  Large scale replications of chunks of the literature, but aren't many (list and explain)
  We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). The ManyLabs series of replications investigating heterogeneity has sampled target studies that are short and compare only two conditions, which is not representative of the psychology literature as a whole. Across Many Labs 1-3, 29 of 51 target effects (57\%) were found to replicate (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) found a roughly 60\% replication rate when they replicated all 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. Those are all the large-scale replication projects of experimental psychology results available at this time. These roughly 170 results are the primary empirical results discussions of replication in pschology have to rely are.
\item
  These rates feel lower than we want
\end{itemize}

Why? Many approaches, no definitive answers.
What makes the replication rates in psychology so low? Knowing what predicts and drives non-replications would let us potentially increase the replication rate, and also calibrate our levels of caution and skepticism toward results. Theoretical, interventional and correlational approaches do not yet provide comprehensive answers.

\begin{itemize}
\tightlist
\item
  Theoretical -- we know people do bad practices and can model how this leads to lower replicability. Requires things we already have ideas about
\end{itemize}

Theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE). There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.

\begin{itemize}
\item
  Interventional -- try things they think will make it better (like not doing bad practices), see what happens. Not everything is intervention prone, need to have strong belief first. Expensive!
  A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate. For instance, across 16 studies, Protzko et al. (\protect\hyperlink{ref-protzko2020}{2020}) showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original. Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.
\item
  Correlational -- markets/etc say there is some predictive value to be had, but don't say if it's transparent and explainable. RP:P.
  Much of the work looking at predictors of replicability has been correlational. Prediction markets and elicitations have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al. 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al. 2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al. 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al. 2019}), but have not identified many concrete predictors that differentiate replications from non-replications. Machine learning approaches CITE similarly show predictive signal, but do not provide explainable predictor variables. In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate CITE . All of these correlational approaches depend on data from replications, generally drawing heavily from the same small set of large-scale replication data points. In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}), so much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P.

  \begin{itemize}
  \tightlist
  \item
    Note that it's correlational, so can't do causality, but still useful for prediction, and as fodder for theory \& intervention. (Interplay between them)
  \end{itemize}
\end{itemize}

What's missing from the conversation and why our approach is good.
* There's been a lot of discussion around replicabilty and it's role and yadda yadda (much overfocused on RP:P results because that's what's available). Growing sophistication and valid points, but we think it misses the mark about what practicing scientists are concerned about.

What does replicability mean? Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al. 2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al. n.d.}).

@@

This framing of replicability matches our methodology.

Rather than sampling at random from some parts of the literature; our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.

We use a subjective replication score as our primary metric. Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex. interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex. replication is p\textless.05 same direction as original). This avoids bright line distinctions and accomodates the range of outcome measures in our diverse set of studies.

All our replications were conducted under short time scales and relatively small budgets, which mimics the constraints many scientists are under when starting new projects. From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints. The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances. Thus, we believe it is relevant to estimate replicability as done by a graduate student with limited resources.

Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.

Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. We investigated predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.

@@

Many different measures can be used to define replication success of an individual statistical result, and there is much discussion over what each measure represents and which make sense (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure. This measure has the benefit that it was applicable across the diverse range of statistical measures and reporting practices present in the sample. It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest. A holistic measure of replication success had been coded for each project when it was turned in at the end of the class. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (26\% of cases).

@@

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at 2.45 times the rate of social psychology studies. Within and between subjects designs were both common, and within replicated 3.35 times as much. Similarly, studies with multiple vignettes replicated 2.62 times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

@@

Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person). While online studies in general show comparable results to studies conducted in person (\protect\hyperlink{ref-crump2013}{\textbf{crump2013?}})TODO MORE CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

@@

While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regularized regression models (see Methods for details; see Supplement for all estimates from all models). The coefficient estimates of the primary model, predicting the subjective replication scores based on all the data, are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients. The general directions of coefficients are consistent with the effects of the predictors in isolation.

Within-subjects designs stand out as the strongest indicator of replicability in the model without statistical predictors (0.55, CrI= {[}-0.01, 2{]}). When statistical predictors are added to the model, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}). Standardized effect size is another strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}). Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.34{]}; effect size 0.97, CrI= {[}0.76, 4.59{]}).

We also ran models predicting whether the replication effect was within the prediction interval as the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals are wide, the general patterns of predictors are similar to the subjective replication models. The strongest predictors are still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).

@@

@@

@@

@@

### 2023-04-26 paper/supplement.Rmd
work on intro and figure 2

Per our pre-registration, we ran a set of 6 models crossing 3 outcome measures (subjective replication score, whether the replication result was within the prediction interval of the original, and p-original on the hypothesis that both came from the same distribution) with 2 sets of predictors (with or without statistical predictors). These 6 models required 3 tiers of data: the subjective replication score without statistical predictors applies to all the data; the p_original and prediction interval models apply to the subset of data with numeric outcomes that can be compared; and the statistical predictor models need the smaller subset of data with p-values and original SMD in particular.

@@

```{r}
do_draws <- function(model){
  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "SMD"))) 
}

>>>>

Per our pre-registration, we ran a set of 6 models crossing 3 outcome measures (subjective replication score, whether the replication result was within the prediction interval of the original, and p-original on the hypothesis that both came from the same distribution) with 2 sets of predictors (with or without statistical predictors). These 6 models required 3 tiers of data: the subjective replication score without statistical predictors applies to all the data; the p_original and prediction interval models apply to the subset of data with numeric outcomes that can be compared; and the statistical predictor models need the smaller subset of data with p-values and original standardized effect size in particular.

@@

```{r}
do_draws <- function(model){
  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size"))) 
}
